Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

\label{sec:XXX} In weak lensing survey, one way to obtain high S/N
ratio is to stack large number of lensing signal together, and calculate
the mean shear map of all these lensing systems. However simply to
stack all the lensing signals would not be the optimal way because
of the amount of information we can obtain from each lensing system
can be very different. The Bayesian inference approach we proposed
allows a natural way to optimally include all the data. Instead of
stacking what we need to do is to propogate the likelihood of the
shear map of each lensing system. The statistical property of all
the lensing systems like the galaxy-mass ,shear-shar correlation function
,in principle can be calculated from these likelihood functions.

>>>>

\label{sec:XXX} In weak lensing survey, one way to obtain high S/N
ratio is to stack large number of lensing signal together, and calculate
the mean shear map of all these lensing systems. However simply to
stack all the lensing signals would not be the optimal way because
of the amount of information we can obtain from each lensing system
can be very different. The Bayesian inference approach we proposed
allows a natural way to optimally include all the data. Instead of
stacking what we need to do is to propogate the likelihood of the
shear map of each lensing system. The statistical property of all
the lensing systems like the galaxy-mass, shear-shar correlation function
, in principle can be calculated from these likelihood functions.
